Programming Assignment 2

### 2015-04-01 paper.tex
Included \begin{document} as required
Defined the Member Assignment section

\documentclass{article}

@@

\section{Member Assignments}

>>>>

\documentclass{article}
\begin{document}

@@

\section{Member Assignments}
All members were involved in some manner in all major area of the project. These
major areas include the paper writup, the presentation creation, and the 
programming. The specific assignements per group member are given below, but no
single member handled an entire area of development.
\subsection{Jonathan Brandt}
\subsubsection{Programming}
Jonathan's programming work was divided between implementation of the 
Hamming/Max network and the creation of centroids for the networks based on a
large number of sample inputs. He was completely responsible for creating the Hamming layer of the Hamming/MAX network, and worked in conjunction with the rest of the team when creating the centroids.

\subsubsection{Project Report}
Jonathan was tasked with the Hamming/Max section? or perhaps the LVQ

\subsubsection{Project Presentation}
NOTHING HE DID NOTHING 0 percent FOR HIM

\subsection{Skyler Manzanares}
\subsubsection{Programming}
Skyler implemented the formatting of centroid images to the weight matrix to be fed into the Hamming/MAX network. He also did extensive work creating the functions that read in and format images. Skyler was also responsible for implementing
the HAM network.

\subsubsection{Project Report}
Skyler created the template for the project report and was in charge of the HAM 
network section and the Member Assignment section.

\subsubsection{Project Presentation}
lulz he ain't done a thing.

\subsection{William Fong}
\subsubsection{Programming}
William worked to creat the Max layer of the Hamming/Max network and coordinate 
inputs and outputs of the various layers, summing all components together to create a working Hamming/Max network. William was also in charge of implementing the BAM network.

\subsubsection{Project Report}
William was tasked to the BAM section.

\subsubsection{Project Presentation}
nuthin.

\end{document}
